Biotic invasions reduce the manageability of mutualistic networks

### 2016-07-10 paper/supp_info.Rmd
rework supplementary info

*Table S3: pearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.*
```{r table alternative assumptions, echo = FALSE, warning = F, message = F, results = "asis"}

@@

# S3: Threshold

>>>>

*Table S3: Spearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.*
```{r table alternative assumptions, echo = FALSE, warning = F, message = F, results = "asis"}

@@

*Table S4: Model selection table for the manageability of studied communities. Type refers to wether the manageability was calculated using mutual dependences or interaction asymetries. "y" and "n" indicate wheter a variable was included in the model or not.*
```{r models, echo = F, message=F, warning=F, results="asis"}
n_driver <- a_m %>%
  dplyr::inner_join(meta) %>%
  dplyr::filter(count == "visitation") %>%
  dplyr::mutate(n_sp = n_pla + n_pol, 
                n_dr = n_sp - n_matched,
                n_dr_p = n_dr / n_sp)

src_bi_w <- n_driver %>%
  dplyr::filter(type == "z-bi" | type == "weight",
                study != "ballantyne") %>%
  dplyr::select(net_name, type, n_dr_p) %>%
  tidyr::spread(type, n_dr_p) %$%
  cor.test(weight, `z-bi`, method = "spearman")

n_driver %<>%
  dplyr::filter(!is.na(inv))

n_driver_wb <- dplyr::filter(n_driver, 
                             type == "z-bi" | type == "weight")

# Models
m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv + type,
          data = n_driver_wb,
          family = "binomial")
m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type,
          data = n_driver_wb,
          family = "binomial")
m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv + type,
          data = n_driver_wb,
          family = "binomial")
m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + type,
          data = n_driver_wb,
          family = "binomial")
m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + type,
          data = n_driver_wb,
          family = "binomial")
m2 <- glm(cbind(n_dr, n_matched) ~ study + type,
          data = n_driver_wb,
          family = "binomial")
m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol) + type,
          data = n_driver_wb,
          family = "binomial")
m4 <- glm(cbind(n_dr, n_matched) ~ n_pla + type,
          data = n_driver_wb,
          family = "binomial")
m5 <- glm(cbind(n_dr, n_matched) ~ n_pol + type,
          data = n_driver_wb,
          family = "binomial")
m6 <- glm(cbind(n_dr, n_matched) ~ inv + type,
          data = n_driver_wb,
          family = "binomial")
m7 <- glm(cbind(n_dr, n_matched) ~ study + inv + type,
          data = n_driver_wb,
          family = "binomial")

mod_table <- MuMIn::model.sel(m0, m_nr, m8, m9, m1, m2, m3, m4, m5, m6, m7) %>%
	as.data.frame() %>% 
	`rownames<-`(NULL) %>%
	dplyr::select(-1) %>% 
	lapply(function(y) {
		if (class(y) == "factor"){
			y <- as.character(y)
			y <- replace(y, y == "+", "y")
			y <- replace(y, is.na(y), "n")
		} 
		if (class(y) == "numeric" & any(is.na(y))){
			y <- replace(y, !is.na(y), "y")
			y <- replace(y, is.na(y), "n")
		}
		y
	}) %>% as.data.frame()

names(mod_table)[1:8] <- c("invaded", "$n_p$", "$n_a$", "study", "type", "$n_p:n_a$", "$n_p/n_a$", "$n_p+n_a$")

mod_table %<>%
	dplyr::mutate(logLik = round(logLik, 1), 
								AICc = round(AICc, 1),
								delta = round (delta, 1),
								weight = round(weight, 3))

mod_table %>% knitr::kable(booktabs = T)
```

\newpage
# S3: Threshold
